CF Registry Analysis

### 2024-02-16 Christine Chan/CF Registry/cf_registry_analysis.qmd
forest plot mostly done
had a better idea for easy forest plots, lol

```{r}
forest_plot <- function(mod, time_varying = NULL, labels = labels) {
  coeff <- tbl_regression(cox_res,
    exponentiate = T,
    pvalue_fun = function(x) x
  ) %>%
    add_n(location = "level") %>%
    as_tibble()
  coeff_n <- tbl_regression(cox_res, exponentiate = T) %>%
    add_n(location = "label") %>%
    as_tibble()
  coeff$N2 <- coeff_n$`**N**`
  # Combine Ns
  coeff <- coeff %>% unite(N, `**N**`, N2, remove = F, na.rm = T)
  # Separate CI column
  coeff$hr <- as.numeric(coeff$`**HR**`)
  coeff$ll <- as.numeric(sapply(str_split(coeff$`**95% CI**`, ", "), "[", 1))
  coeff$ul <- as.numeric(sapply(str_split(coeff$`**95% CI**`, ", "), "[", 2))
  # Add N to names
  coeff$names <- paste0(coeff$`**Characteristic**`, " (N = ", coeff$N, ")")
  coeff$names <- ordered(coeff$names,
    levels = unique(coeff$names)
  )
  # P values
  coeff$sig <- coeff$`**p-value**` < 0.05
  coeff$p <- style_pvalue(coeff$`**p-value**`)
  # Row types
  coeff$type <- "level"
  coeff$type[!is.na(coeff$N2)] <- "variable"
  coeff$type[!is.na(coeff$`**N**`) & is.na(coeff$`**HR**`)] <- "reference"
  # HR label
  coeff$hr_lab <- paste0(coeff$`**HR**`, " (", coeff$`**95% CI**`, ")")
  coeff$hr_lab[coeff$hr_lab == "NA (NA)"] <- NA
  coeff$hr_lab[coeff$type == "reference"] <- "Reference"
  # Plot
  p_left <- ggplot(coeff, aes(y = fct_rev(names))) +
    geom_text(aes(x = 0, label = names),
      hjust = 0,
      fontface = ifelse(coeff$type == "variable", "bold", "plain")
    ) +
    geom_text(aes(x = 1, label = hr_lab), hjust = 0) +
    theme_void() +
    coord_cartesian(xlim = c(0, 2)) +
    geom_stripes()
  p <- ggplot(coeff, aes(y = fct_rev(names))) +
    geom_point(aes(x = hr), shape = 15, size = 3) +
    geom_linerange(aes(xmin = ll, xmax = ul)) +
    geom_vline(xintercept = 1, linetype = "dashed") +
    xlab("Hazard Ratio") +
    theme_classic() +
    theme(
      axis.line.y = element_blank(),
      axis.ticks.y = element_blank(),
      axis.text.y = element_blank(),
      axis.title.y = element_blank(),
      axis.line.x = element_blank()
    ) +
    geom_stripes()
  # p values
  p_right <- ggplot(coeff, aes(y = fct_rev(names))) +
    geom_text(aes(x = 0, label = p),
      hjust = 0,
      fontface = ifelse(coeff$sig, "bold", "plain")
    ) +
    theme_void() +
    geom_stripes()
  # Layout
  p_left + p + p_right +
    plot_layout(widths = c(1, 2, 0.25), guides = "collect") &
    theme(plot.margin = margin(0, 0, 0, 0, "pt"))
  # Return each plot separately - will need to be combined outside of the function
  return(c(p_left, p, p_right))
}
```

>>>>

```{r}
forest_plot <- function(mod, time_varying = NULL, labels = labels) {
    coeff <- tbl_regression(mod,
        pvalue_fun = function(x) x
    ) %>%
        add_n(location = "level") %>%
        as_tibble()
    coeff_n <- tbl_regression(mod, exponentiate = T) %>%
        add_n(location = "label") %>%
        as_tibble()
    coeff$N2 <- coeff_n$`**N**`
    # Combine Ns
    coeff <- coeff %>% unite(N, `**N**`, N2, remove = F, na.rm = T)
    # Exponentiate
    coeff$hr <- exp(as.numeric(coeff$`**log(HR)**`))
    coeff$exp.ll <- exp(as.numeric(sapply(str_split(coeff$`**95% CI**`, ", "), "[", 1)))
    coeff$exp.ul <- exp(as.numeric(sapply(str_split(coeff$`**95% CI**`, ", "), "[", 2)))
    # Add N to names
    coeff$names <- paste0(coeff$`**Characteristic**`, " (N = ", coeff$N, ")")
    coeff$names <- ordered(coeff$names,
        levels = unique(coeff$names)
    )
    # P values
    coeff$sig <- coeff$`**p-value**` < 0.05
    coeff$p <- style_pvalue(coeff$`**p-value**`)
    # Row types
    coeff$type <- "level"
    coeff$type[!is.na(coeff$N2)] <- "variable"
    coeff$type[!is.na(coeff$`**N**`) & is.na(coeff$`**HR**`)] <- "reference"
    # HR label
    coeff$hr_lab <- paste0(coeff$`**HR**`, " (", coeff$`**95% CI**`, ")")
    coeff$hr_lab[coeff$hr_lab == "NA (NA)"] <- NA
    coeff$hr_lab[coeff$type == "reference"] <- "Reference"
    # Plot
    p_left <- ggplot(coeff, aes(y = fct_rev(names))) +
        geom_text(aes(x = 0, label = names),
            hjust = 0,
            fontface = ifelse(coeff$type == "variable", "bold", "plain")
        ) +
        geom_text(aes(x = 1, label = hr_lab), hjust = 0) +
        theme_void() +
        coord_cartesian(xlim = c(0, 1.5)) +
        geom_stripes()
    p <- ggplot(coeff, aes(y = fct_rev(names))) +
        geom_point(aes(x = hr), shape = 15, size = 3) +
        geom_linerange(aes(xmin = ll, xmax = ul)) +
        geom_vline(xintercept = 1, linetype = "dashed") +
        xlab("Hazard Ratio") +
        theme_classic() +
        theme(
            axis.line.y = element_blank(),
            axis.ticks.y = element_blank(),
            axis.text.y = element_blank(),
            axis.title.y = element_blank(),
            axis.line.x = element_blank()
        ) +
        geom_stripes()
    # p values
    p_right <- ggplot(coeff, aes(y = fct_rev(names))) +
        geom_text(aes(x = 0, label = p),
            hjust = 0,
            fontface = ifelse(coeff$sig, "bold", "plain")
        ) +
        theme_void() +
        geom_stripes()
    # Layout
    final_p = p_left + p + p_right +
        plot_layout(widths = c(1, 2, 0.25), guides = "collect") &
        theme(plot.margin = margin(0, 0, 0, 0, "pt"))
    # Return
    return(final_p)
}
```
